Supplementary Materials

### 2020-05-13 analysis/analysis.Rmd
Finally fixed first figure to have a proper caption!

library(bookdown)
library(tidyverse)
library(brms)
library(tidybayes)
library(ggridges)
library(latex2exp)
library(see)
library(ggthemes)
library(patchwork)

@@

Use multiple cores and set number of iterations. 
```{r}
options(mc.cores = parallel::detectCores())
n_iter <- 10000

@@

![RMS data from two of the wallpaper groups, P2 and P4M. Odd harmonics are shown in A and B, while even harmonic data are shown in C and D, and occipital and parietal regions of interest are shown in dark nad light gray, respectively. The two groups elicit very different response amplitudes for odd harmonics over occipital cortex, but for even harmonics those differences are much less pronounced.](../figures/occTopo_merged.png)

>>>>

library(bookdown)
library(tidyverse)
library(brms)
library(tidybayes)
library(ggridges)
library(latex2exp)
library(see)
library(ggthemes)
library(patchwork)
library(magick)

@@

```{r}
# Use multiple cores and set number of iterations. 
options(mc.cores = parallel::detectCores())
n_iter <- 10000

@@

```{r, fig.cap = "RMS data from two of the wallpaper groups, P2 and P4M. Odd harmonics are shown in A and B, while even harmonic data are shown in C and D, and occipital and parietal regions of interest are shown in dark nad light gray, respectively. The two groups elicit very different response amplitudes for odd harmonics over occipital cortex, but for even harmonics those differences are much less pronounced."}
plt <- cowplot::ggdraw() +
  cowplot::draw_image("../figures/occTopo_merged.png")
print(plt)

```
at
